---
title: "First R assignment"
author: "Burkan Bereketoglu"
date: "October 26, 2021"
output: html_document
---
As a first R assignment I decide to do a simple data package on R itself.

Here is the data.
```{r}
library(datasets)

data("airquality")

summary(airquality)

plot(airquality$Ozone,airquality$Solar.R, 
     main="Ozone vs Solar Radiation",
        xlab="Ozone",
        ylab="Solar Radiaton",
     col = c("blue","red"))
```

Red color represents solar rays, Blue color represents Blue sky and from that ozone.

```{r, echo=FALSE}
names(iris) <- tolower(names(iris))
library(datasets)
library(tidyverse)
library(tibble)

data("iris")
summary(iris)

iris_vers_sepal_length <- as_tibble(iris %>% 
  select(Sepal.Length) %>% 
  filter(iris$Species == "versicolor") %>%
  arrange(desc(Sepal.Length)))
iris_vers_sepal_length

iris_seto_sepal_length <- as_tibble(iris %>% 
  select(Sepal.Length) %>% 
  filter(iris$Species == "setosa",) %>%
  arrange(desc(Sepal.Length)))
iris_seto_sepal_length

iris_virg_sepal_length <- as_tibble(iris %>% 
  select(Sepal.Length) %>% 
  filter(iris$Species == "virginica",) %>%
  arrange(desc(Sepal.Length)))
iris_virg_sepal_length


sapply(iris_virg_sepal_length, mean, na.rm = TRUE)
lapply(iris_vers_sepal_length, mean, na.rm = TRUE)
sapply(iris_seto_sepal_length, mean, na.rm = TRUE)
cor(iris_vers_sepal_length,iris_seto_sepal_length)
cor(iris_vers_sepal_length,iris_virg_sepal_length)
cor(iris_virg_sepal_length,iris_seto_sepal_length)

```

The Sepal Length is highly correlated between species which can mean that Sepal Length is something inherited from the genus not species.
```{r, echo=FALSE}

names(iris) <- tolower(names(iris))
library(datasets)
library(tidyverse)
library(tibble)

data("iris")

iris_sepal <- as_tibble(iris %>% 
  select(Sepal.Length, Sepal.Width, Species) %>% 
  arrange(desc(Sepal.Length)))
iris_sepal

iris_vers_sepal <- as_tibble(iris %>% 
  select(Sepal.Length, Sepal.Width, Species) %>% 
  filter(iris$Species == "versicolor") %>%
  arrange(desc(Sepal.Length)))
iris_vers_sepal

iris_seto_sepal <- as_tibble(iris %>% 
  select(Sepal.Length, Sepal.Width, Species) %>% 
  filter(iris$Species == "setosa") %>%
  arrange(desc(Sepal.Length)))
iris_seto_sepal

iris_virg_sepal <- as_tibble(iris %>% 
  select(Sepal.Length, Sepal.Width, Species) %>% 
  filter(iris$Species == "virginica") %>%
  arrange(desc(Sepal.Length)))
iris_virg_sepal

plot_test <- ggplot(iris_sepal, aes(x= Sepal.Length, y = Sepal.Width, colour = Species)) +
  geom_point() +
  geom_point() +
  geom_point() +
  geom_line() +
  xlab(label = "Sepal Length") +
  ylab(label = "Sepal Width")+
  ggtitle("Width vs Length")

plot_test +
  geom_smooth(method="loess", color="darkgreen", fill="blue", alpha=0.2)+
  scale_color_manual(values = c("#E69F00","#800080", "#808080"))

```

From the plot we can see that setosa differs from the length and height compared to other to species of iris genus.

```{r, echo=FALSE}
names(iris) <- tolower(names(iris))
library(datasets)
library(tidyverse)
library(tibble)

data("iris")

filtered_species <- iris %>%
  filter(Species %in% c("virginica","versicolor","setosa"), Petal.Length > 1.3, Petal.Width > 0.1) %>%
  select(-(c(Sepal.Length,Sepal.Width))) %>%
  arrange(desc(Petal.Length)) %>%
  mutate(Petal.Area = Petal.Length * Petal.Width) %>%
  group_by(Species) %>%
  summarize(meanLength = mean(Petal.Length), meanWidth = mean(Petal.Width), TotalNumber= n())

filtered_species
```